MTBD models with partner notification

### 2023-06-12 article/article.tex
cherry test on simulated data

\subsection{Performance on simulated data}
To illustrate the PN test performance, we applied it to the trees simulated under BD and under BDPn models.

... details coming soon ...

@@

To assess the performance of our maximum-likelihood estimator for the BD-PN model, we simulated 100 trees with 5\,000--10\,000 tips under the BD-PN model with our tree simulator. For each tree the parameter values were drawn randomly within the following bounds:
$R_e = \frac{{\lambda}}{{\psi}} \in ]1, 5]$, 
removal rate $\psi \in ]1 / 20, 1 / 5]$,
ratio between the partner removal rate after notification and the removal rate $\frac{\psi_n}{\psi} \in ]10, 100]$,
sampling probability $\rho \in ]0.01, 0.9]$,
partner notification probability $\rho_n \in ]0.1, 0.9]$.
We applied bdpn to each of the trees three times: fixing each of the BD parameters ($\lambda,\psi$ or $\rho$) to its real value (for identifiability).

>>>>

\subsection{Performance on simulated data}
To illustrate the PN test performance, we applied it to the trees simulated under BD and under BD-PN models. We simulated 100 trees with 5\,000--10\,000 tips under the BD-PN model with our tree simulator. For each tree the parameter values were drawn randomly within the following bounds:
$R_e = \frac{{\lambda}}{{\psi}} \in ]1, 5]$, 
removal rate $\psi \in ]1 / 20, 1 / 5]$,
ratio between the partner removal rate after notification and the removal rate $\frac{\psi_n}{\psi} \in ]10, 100]$,
sampling probability $\rho \in ]0.01, 0.9]$,
partner notification probability $\rho_n \in ]0.1, 0.9]$. We also simulated 100 trees of 5\,000--10\,000 tips under the BD model. For each tree in the BD data set the parameter values ($\lambda, \psi,$ and $\rho$) were the same as the ones selected for the corresponding tree of the BD-PN dataset.

We then run the PN tests on each tree of the both datasets. For all the trees in the BD dataset the PN test value was above $0.05$ and varied between $0.33$ and $0.63$ (i.e. 100\% true negative results). For 97 (out of 100) trees in the BD-PN dataset the PN test value was below $0.05$ (i.e. 97\% true positive and 3\% false negative results).
Our test therefore showed absolute specificity and high sensitivity.

@@

To assess the performance of our maximum-likelihood estimator for the BD-PN model, we used the 100 trees with 5\,000--10\,000 tips simulated under the BD-PN model as described in the "PN test" section.

We applied bdpn to each of the trees three times: fixing each of the BD parameters ($\lambda,\psi$ or $\rho$) to its real value (for identifiability).
